### 2018-09-12 doc/paper.tex
Removing subsections from introduction.
Changed intro to just introduce the problem.
The "solution" is introduced later on (at the start of the
limitations paragraphs.)

In this paper, an algorithm for conservative solution transfer between curved
meshes will be described. This has practical applications to many methods in
computational physics. For example, by allowing the underyling
computational domain to change during a simulation, computational
effort can be focused dynamically to resolve sensitive features
of a numerical solution. Mesh adaptivity, this in-flight change in the mesh,
requires translating the numerical solution from the old mesh to the new,
i.e. solution transfer. As another example, Lagrangian or particle-based
methods treat each node in the mesh as a particle and so with each timestep the
mesh travels \emph{with} the fluid.
However, over (typically limited) time the mesh
becomes distorted and suffers a loss in element quality which causes
catastrophic loss in the accuracy of computation. To overcome this, the
domain must be remeshed or rezoned and the solution must be
transferred (remapped) onto the new mesh configuration. A few scenarios
where solution transfer is necessary will be considered below
to motivate the ``black box'' solution transfer algorithm.

@@

\subsection{Lagrangian Methods}

@@

\subsection{Remeshing and Adaptivity}

@@

\subsection{High-order Meshes}

@@

\subsection{Multiphysics and Comparing Methods}

@@

\subsection{Local versus Global Transfer}

@@

\subsection{Limitations}

@@

The method described in this paper only applies to meshes in \(\reals^2\).
Application to meshes in \(\reals^3\) is a direction for future research,
though the geometric kernels (see Chapter~\ref{sec:bezier-intersection})
become significantly more challenging to describe and implement. In
addition, the method will assume that every element in the
target mesh is contained in the donor mesh. This ensures that the solution
transfer is \emph{interpolation}. In the case where all target elements are
partially covered, \emph{extrapolation} could be used to extend a solution
outside the domain, but for totally uncovered elements there is no clear
correspondence to elements in the donor mesh.

@@

\subsection{Overview}

>>>>

Solution transfer between meshes is a common problem that
has practical applications to many methods in
computational physics. For example, by allowing the underyling
computational domain to change during a simulation, computational
effort can be focused dynamically to resolve sensitive features
of a numerical solution. Mesh adaptivity, this in-flight change in the mesh,
requires translating the numerical solution from the old mesh to the new,
i.e. solution transfer. As another example, Lagrangian or particle-based
methods treat each node in the mesh as a particle and so with each timestep the
mesh travels \emph{with} the fluid.
However, over (typically limited) time the mesh
becomes distorted and suffers a loss in element quality which causes
catastrophic loss in the accuracy of computation. To overcome this, the
domain must be remeshed or rezoned and the solution must be
transferred (remapped) onto the new mesh configuration. A few scenarios
where solution transfer is necessary will be considered below
to motivate the ``black box'' solution transfer algorithm.

@@

@@

@@

@@

@@

@@

@@

In this paper, an algorithm for conservative solution transfer between curved
meshes will be described. This method applies to meshes in \(\reals^2\).
Application to meshes in \(\reals^3\) is a direction for future research,
though the geometric kernels (see Chapter~\ref{sec:bezier-intersection})
become significantly more challenging to describe and implement. In
addition, the method will assume that every element in the
target mesh is contained in the donor mesh. This ensures that the solution
transfer is \emph{interpolation}. In the case where all target elements are
partially covered, \emph{extrapolation} could be used to extend a solution
outside the domain, but for totally uncovered elements there is no clear
correspondence to elements in the donor mesh.

@@
